Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-20 WSSSPE1_report/WSSSPE1_summary_report.tex
changed a footnote to bib

\subsubsection{Measuring community}
How might a project know when it has built a sustainable community?  How might an outsider be able to assess the activity and sustainability of that community?  These questions have been partially addressed in the literature.  For example, a key metric in online communities in general is the cross-over point where there are more external contributors than internal ones. Richard Millington's book ``Buzzing Communities'' does an excellent job of outlining these measures, drawing on online communities research in an accessible manner~\cite{millington_buzzing_2012}. Some participants in the workshop have since prepared online materials outlining current and future practices in measurement of scientific software and its ecosystem\footnote{\url{https://sites.google.com/site/scientificsoftwaremetrics/}}. \katznote{please change to cite}

>>>>

\subsubsection{Measuring community}
How might a project know when it has built a sustainable community?  How might an outsider be able to assess the activity and sustainability of that community?  These questions have been partially addressed in the literature.  For example, a key metric in online communities in general is the cross-over point where there are more external contributors than internal ones. Richard Millington's book ``Buzzing Communities'' does an excellent job of outlining these measures, drawing on online communities research in an accessible manner~\cite{millington_buzzing_2012}. Some participants in the workshop have since prepared online materials outlining current and future practices in measurement of scientific software and its ecosystem~\cite{metrics-web}.
%\footnote{\url{https://sites.google.com/site/scientificsoftwaremetrics/}}. \katznote{please change to cite}
